\documentclass{article}

\input{preamble_arXiv}

\title{Research diary Vinícius PhD}

\date{\today}

\begin{document}

\maketitle

\section*{2025-06-10}

TODO for next meeting:
\begin{itemize}
    \item[$\checkmark$] Define $f_0$
    \item[$\checkmark$] Define bold h
    \item[$\checkmark$] Introduce stretchers before introducing the statistic $T_n$
    \item[$\checkmark$] Use $\rho(h)$
    \item[$\checkmark$] Use independence estimator $f_0$
    \item[$\checkmark$] Do not use $i$ as a component index
    \item[$\checkmark$] Expectation of $f$ equal to expectation of $f_0$
    \item[$\checkmark$] Mention product kernel as a definition
    \item[$\checkmark$] Use \verb|\b| whenever possible
    \item[$\checkmark$] Fix $c$ (normalizing constant)
    \item[$\checkmark$] Define $L_u$ earlier (fix swapped notation)
    \item[$\checkmark$] Remove references
    \item [$\checkmark$] Remove compilation errors in the draft
    \item Aim for application of Lemma 1 in the article
    \item Use Taylor expansion (done in the lemma 1 paper)
    \item [$\checkmark$] Properly introduce the notation and the introduction of the density stretchers. Define lambda and other necessary notation as they appear in the polysphere paper.
    \item[$\checkmark$] Split sections and better organize the paper
    \item [$\checkmark$] Apply law of large numbers to $I_{n1}^{(1)}$ as we did on the board
    \item [$\checkmark$] Polysphere paper: variance of $f_0$, read sections 2–3
    \item[$\checkmark$] Add conjecture on variance of terms generalizing Lemma 7 by adding bandwidth multipliers raised to their dimensions
    \item [$\checkmark$] Write the conjecture of the main theorem, its proof using the lemmas, assuming they hold
    \item [$\checkmark$] Leave the proof of the lemma for $I_{n1}^{(2)}$ aside
\end{itemize}

\section*{2025-06-13}

TODO for next meeting:
\begin{itemize}
    \item [$\checkmark$] Re-read the paperwriting document to avoid mistakes while writing
    \item [$\checkmark$] Introduce lambda and rho at the beginning of the paper, in section 2; mention the normalizing constant
    \item [$\checkmark$]Change references to match the format used in directionalstats.bib
    \item [$\checkmark$]Add the new references to the file no-directional-stats
    \item [$\checkmark$] Be aware that I will have to introduce context in section 1 (spheres, goals of the work, etc.)
    \item [$\checkmark$] List the assumptions being made, using the polysphere paper
    \item [$\checkmark$] Mistake: I used the estimator’s variance instead of the kernel’s variance
    \item [$\checkmark$]Change notation in the estimators: $;h_j$
    \item [$\checkmark$]Add in section 2 results from the polysphere paper
    \item [$\checkmark$] Look at the 2015 hypersphere paper to see how they computed $Var(Z_{ni})$
    \item [$\checkmark$] \textbf{Put the main theorem and its proof based on calling lemmas. Conjecture the lemmas based on the 2015 paper structure, if needed. Then we prove the lemmas.}
\end{itemize}

\section*{2025-06-17}

TODO for next meeting:
\begin{itemize}
    \item \textbf{Do all the previous points from the previous meetings.}
    \item [$\checkmark$] Read the proof of the independence test in G-P et al (2015, Statistica Sinica, see the arXiv).
    \item [$\checkmark$] Update the conjectures on the lemmas based on the previous points.
    \item [$\checkmark$] Evaluate the variance of $Z_{ni}$ through the paper on CLT paper directional variables.
    \item [$\checkmark$] Finish the proof of the main theorem (show that $N_n$ is dominant).
    \item [$\checkmark$] Correct variance of the last two terms.
\end{itemize}

\section*{2025-06-25}
\begin{itemize}
    \item [$\checkmark$] Adopt the notation used in García-Portugués et al (2015) to decompose the statistic in the three terms in the independence test chapter.
    \item [$\checkmark$] Add the asymptotic equivalence $\int_{\Sr} L_{\bh}^k(\bx,\by) g(\by)\,\rd\by\asymp  \dots$ as a lemma.
    \item [$\checkmark$] Recalculate the variance of $I_{n1}^{(1)}$ (which will have a new name after notation change) using the lemma mentioned in the previous item, using as basis the calculations done by Eduardo in the notes.
    \item [$\checkmark$] Note that the results of this project must be coherent with the results present in García-Portugués et al (2015), considering that the directional-linear can be viewed as a particular case ($r=2$, $(d_1,d_2)=(q, 1)$ and $(h_1,h_2)=(h,g)$ --- in this case $\rho(\bh)=h^q g$).
\end{itemize}

\section*{2025-07-15}

\begin{itemize}
    \item [$\checkmark$] Put conjecture Lemma 3.2
    \item [$\checkmark$] Prove the hypothesis of the lemma of Hall, used in the proof of Lemma 3.1.
    \item Proving and presenting in a clear form Theorem 3.1
    \item Advance in the proofs of Lemmas 3.5 and 3.6
    \item [$\checkmark$] Rewrite the theorem using $T_n$ notation.
\end{itemize}

\end{document}